Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia

### 2017-06-28 doc/manuscript/manuscript.Rmd
update manuscript with correct bibliography

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amadarasa
    email: bamadarasa2@unl.edu
    affiliation: 1
  - name: R. Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
# author_summary: |
#   Lorem ipsum dolor sit amet, consectetur adipiscing elit.
header-includes: >
  \usepackage{indentfirst}
bibliography: mybibfile.bib
output: 
  rticles::peerj_article:
    citation_package: natbib
    base_format: bookdown::pdf_document2 # for using \@ref()
---

@@

![Network of populations (nodes/circles) and their shared multilocus haplotypes (MLG) (edges/lines) genotyped over 11 loci. 
Each node is labeled with **name (number of MLGs shared/number of MLGs total).** 
The shade and area of the nodes are proportional to the number of unique MLGs within the node and the inner nodes are proportional to the number of private MLGs to the region. 
Each edge represents a single MLG where its thickness represents the number of populations that share the MLG and the shade represents the value of $P_{sex}$, or the probability of encountering that MLG from two independent meiotic events.
](../../results/figures/publication/Figure3Z.pdf){#community-graph width=50%}

>>>>

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amadarasa
    email: bamadarasa2@unl.edu
    affiliation: 1
  - name: R. Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
# author_summary: |
#   Lorem ipsum dolor sit amet, consectetur adipiscing elit.
header-includes: >
  \usepackage{indentfirst}
bibliography: ssc_bibliography.bib
output: 
  rticles::peerj_article:
    citation_package: natbib
    base_format: bookdown::pdf_document2 # for using \@ref()
---

@@

<!-- community graph figure -->

![
Network of populations (nodes/circles) and their shared multilocus haplotypes (MLG) (edges/lines) genotyped over 11 loci. 
Each node is labeled with **name (number of MLGs shared/number of MLGs total).** 
The shade and area of the nodes are proportional to the number of unique MLGs within the node and the inner nodes are proportional to the number of private MLGs to the region. 
Each edge represents a single MLG where its thickness represents the number of populations that share the MLG and the shade represents the value of $P_{sex}$, or the probability of encountering that MLG from two independent meiotic events.
](../../results/figures/publication/Figure3Z.pdf){#community-graph width=50%}

<!-- end fig -->
